---
title: "Project Proposal STAT 405"
author: "Kelly-Ann Lessard, Qinxin Liu, and Griffin McDonald"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Repository
The link for the public repository containing our project is <https://github.com/qinxinLiu/STAT-405-Project.git>.


## Datasets

### Preferred Dataset

Our preferred dataset is Pharmacokinetic dataset containing 16 subjects with single bolus dose. It has 112 rows and 8 variables. The variables are:
  
- Subject: The ID of the subject
- Nom_Time: The nominal time (intended time)
- Act_Time: The actual time
- Amount: The amount of drug given
- Conc: The drug concentration in the blood
- Age: The age of the subject
- BodyWeight: The weight of the subject
- Gender: The gender of the subject (male or female)

The dataset comes from Centera University. It can be found in the *Certera.RsNLME* package. The URL of the documentation of this package is <https://rdrr.io/cran/Certara.RsNLME/man/pkData.html>. Here is a preview of the dataset:

````{r data1, echo=FALSE, warning=FALSE}
#install.packages("Certara.RsNLME") run in console
library(Certara.RsNLME)
head(pkData)
````

### Backup Dataset

Our backup dataset is Pharmacokinetics of Theophylline. It contains 132 rows and 5 variables. The variables are:

- Subject: The ID of subject
- Wt: The weight of the subject
- Dose: The amount of drug intake
- Time: The measurement time of drug concentration 
- conc: The drug concentration in the blood

The dataset is obtained from Kaggle. It can be accessed through the URL: <https://www.kaggle.com/datasets/ukveteran/pharmacokinetics-of-theophylline>. The first few rows of the dataset are:


```{r data2, echo=FALSE}
data = read.csv("data/Theoph.csv")
data <- data[, -1]
head(data)
```


## Scientific Question
How does inter-individual variability impact the pharmacokinetic profile of the study drug, and how do sampling-based versus optimization-based Bayesian inference methods compare in efficiency and accuracy when estimating these hierarchical population parameters?


## Methodology
We will fit two models: a one-compartment pharmacokinetics model and a mixed-effects model. 

### One-Compartment Pharmacokinetics Model
For the one-compartment pharmacokinetics model, we will compute the posterior using two methods: HMC (in Stan) and variational inference.


### Mixed-Effects Model


## Contribution Plan

