---
title: "Project Proposal STAT 405"
<<<<<<< HEAD
author: "Kelly-Ann Lessard, Qinxin Liu, and Griffin McDonald"
date: "`r Sys.Date()`"
output: html_document---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Repository
The link for the public repository containing our project is <https://github.com/qinxinLiu/STAT-405-Project.git>.


## Datasets

Our preferred dataset is Pharmacokinetic dataset containing 16 subjects with single bolus dose. It has 112 rows and 8 variables. The variables are:
  
- Subject: The ID of the subject
- Nom_Time: The nominal time (intended time)
- Act_Time: The actual time
- Amount: The amount of drug given
- Conc: The drug concentration in the blood
- Age: The age of the subject
- BodyWeight: The weight of the subject
- Gender: The gender of the subject (male or female)

The dataset comes from Centera University. It can be found in the *Certera.RsNLME* package. The URL of the documentation of this package is <https://rdrr.io/cran/Certara.RsNLME/man/pkData.html>. 

```{r data1, echo=TRUE}
install.packages("Certara.RsNLME")
library(Certara.RsNLME)
head(pkData)
```

Our backup dataset is ####. **Description ####** It's URL is <https://www.kaggle.com/datasets/ukveteran/pharmacokinetics-of-theophylline>. 

```{r data2, echo=TRUE}
data = read.csv("Downloads/Theoph.csv")
data <- data[, -1]
head(data)
```


## Scientific Question
How does inter-individual variability impact the pharmacokinetic profile of the study drug, and how do sampling-based versus optimization-based Bayesian inference methods compare in efficiency and accuracy when estimating these hierarchical population parameters?
**Explanation ####**


## Methodology
**Plan ####**


## Contribution Plan