---
title: "Project Proposal STAT 405"
author: "Kelly-Ann Lessard, Qinxin Liu, and Griffin McDonald"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Repository
The link for the public repository containing our project is <https://github.com/qinxinLiu/STAT-405-Project.git>.


## Datasets

Our preferred dataset is Pharmacokinetic dataset containing 16 subjects with single bolus dose. It has 112 rows and 8 variables. The variables are:
  
- Subject: The ID of the subject
- Nom_Time: The nominal time (intended time)
- Act_Time: The actual time
- Amount: The amount of drug given
- Conc: The drug concentration in the blood
- Age: The age of the subject
- BodyWeight: The weight of the subject
- Gender: The gender of the subject (male or female)

The dataset comes from Centera University. It can be found in the *Certera.RsNLME* package. The URL of the documentation of this package is <https://rdrr.io/cran/Certara.RsNLME/man/pkData.html>. 

````{r data1, echo=FALSE}
#install.packages("Certara.RsNLME") run in console
library(Certara.RsNLME)
head(pkData)
````
Our backup dataset is ####. **Description ####** It's URL is <https://www.kaggle.com/datasets/ukveteran/pharmacokinetics-of-theophylline>. 

```{r data2, echo=FALSE}
#head(data_df) ####
data = read.csv("Downloads/Theoph.csv")
data <- data[, -1]
head(data)
#  Subject   Wt Dose Time  conc
#1       1 79.6 4.02 0.00  0.74
#2       1 79.6 4.02 0.25  2.84
#3       1 79.6 4.02 0.57  6.57
#4       1 79.6 4.02 1.12 10.50
#5       1 79.6 4.02 2.02  9.66
#6       1 79.6 4.02 3.82  8.58
```


## Scientific Question
**Explanation ####**



## Methodology
We will fit two models: a one-compartment pharmacokinetics model and a mixed-effects model. 

### One-Compartment Pharmacokinetics Model
For the one-compartment pharmacokinetics model, we will compute the posterior using two methods: HMC (in Stan) and variational inference.


### Mixed-Effects Model


## Contribution Plan