---
title: "Project Proposal STAT 405"
<<<<<<< HEAD
author: "Kelly-Ann Lessard, Qinxin Liu, and Griffin McDonald"
date: "`r Sys.Date()`"
output: html_document---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Repository
The link for the public repository containing our project is <https://github.com/qinxinLiu/STAT-405-Project.git>.


## Datasets

Our preferred dataset is Pharmacokinetic dataset containing 16 subjects with single bolus dose. It has 112 rows and 8 variables. The variables are:
- Subject: The ID of the subject
- Nom_Time: Nominal Time
- Act_Time: Actual Time
- Amount: Amount of dose
- Conc: Observations of drug concentration in blood
- Age: Age
- BodyWeight: Body weight
- Gender: Gender ("male", "female")

It is in the Certera.RsNLME package. The URL of the documentation of this package is <https://rdrr.io/cran/Certara.RsNLME/man/pkData.html>. 

```{r data1, echo=FALSE}
#head(data_df) ####
```

Our backup dataset is ####. **Description ####** It's URL is <https://www.kaggle.com/datasets/ukveteran/pharmacokinetics-of-theophylline>. 

```{r data2, echo=FALSE}
#head(data_df) ####
```


## Scientific Question
**Explanation ####**


## Methodology
**Plan ####**


## Contribution Plan
