---
title: "Project Proposal STAT 405"
author: "Kelly-Ann Lessard, Qinxin Liu, and Griffin McDonald"
bibliography: reference.bib
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Repository
The link for the public repository containing our project is <https://github.com/qinxinLiu/STAT-405-Project.git>.


## Datasets

### Preferred Dataset

Our preferred dataset is Pharmacokinetic dataset containing 16 subjects with single bolus dose. It has 112 rows and 8 variables. The variables are:
  
- Subject: The ID of the subject
- Nom_Time: The nominal time (intended time)
- Act_Time: The actual time
- Amount: The amount of drug given
- Conc: The drug concentration in the blood
- Age: The age of the subject
- BodyWeight: The weight of the subject
- Gender: The gender of the subject (male or female)

The dataset comes from Centera University. It can be found in the *Certera.RsNLME* package. The URL of the documentation of this package is <https://rdrr.io/cran/Certara.RsNLME/man/pkData.html>. Here is a preview of the dataset:

````{r data1, echo=FALSE, warning=FALSE}
#install.packages("Certara.RsNLME") run in console
library(Certara.RsNLME)
head(pkData)
````

### Backup Dataset

Our backup dataset is Pharmacokinetics of Theophylline. It contains 132 rows and 5 variables. The variables are:

- Subject: The ID of subject
- Wt: The weight of the subject
- Dose: The amount of drug intake
- Time: The measurement time of drug concentration 
- conc: The drug concentration in the blood

The dataset is obtained from Kaggle. It can be accessed through the URL: <https://www.kaggle.com/datasets/ukveteran/pharmacokinetics-of-theophylline>. The first few rows of the dataset are:


```{r data2, echo=FALSE}
data = read.csv("data/Theoph.csv")
data <- data[, -1]
head(data)
```


## Scientific Question
How does inter-individual variability impact the pharmacokinetic profile of the study drug, and how do sampling-based versus optimization-based Bayesian inference methods compare in efficiency and accuracy when estimating these hierarchical population parameters?


## Methodology
We are interested in implementing a one-compartment pharmacokinetics models. Two versions of this model will compared: a complete pooling model and a hierarchical one. Moreover, two different posterior inference methods will be used.

### One-Compartment Pharmacokinetics Model
Pharmacokinetics models are used to describe the change in drug concentration in the body over time. A one-compartment model assumes that the patient's body is one big compartment. Thus the drug concentration is uniform throughout it. The complete pooling model assumes that there is no variability between the individuals, whereas the hierarchical model allows for this variability. To assess the quality of the fit of the model, posterior predictive checks will be performed. Furthermore, the predictive performance of both models will be compared using leave-one-out cross-validation.

For the bolus dataset, the drug is administered intravenously, so the one-compartment model only includes a clearance process. The equations of one-compartment model is (@margossian2022torsten1):
$$u'_{cent}(t) = - \frac{CL}{V_{cent}}u_{cent}(t).$$
In contrast, for the Theophylline dataset, the drug is administered orally, the model will include an absorption stage in gut. The equations are (@margossian2022torsten1):
$$u'_{gut}(t) = -k_a u_{gut}(t),$$
$$u'_{cent}(t) = -k_a u_{gut}(t) - \frac{CL}{V_{cent}}u_{cent}(t).$$
Here, $u(t)$ denotes the drug mass ($mg$) at the time $t$ and the corresponding concentration is given by: $$ \text{conc}_{cent}(t) = \frac{u_{cent}(t)}{V_{cent}}.$$
The model parameters are the absorption rate $k_a$ ($h^{-1}$), the volume of compartment $V$ ($L$),and the clearance rate $CL$ ($L/h$). The main difference between complete pooling and hierarchical modeling lies in how these parameters are modeled.

### Posterior Inference Methods
The two posterior inference methods that will be compared are: Hamiltonian Monte Carlo (a sampling-based method), implemented in Stan, and variational inference (an optimization-based method). Convergence of HMC will be assessed with the effective sample size and trace plots. For the variational inference, we will look at the ELBO convergence. The runtime and posterior variance of the two posterior inference methods will be compared.


## Contribution Plan
All members will work on all parts of the assignment, however the Variational inference will be more heavily worked on by Kelly-Ann and Griffin, and the HMC by Jessie. The writeup will be split into segments (ie intro, HMC+Varitaional methods, choices of priors, analysis of posteriors, conclusion) and divided equally as well.

## References